Rbans-output

### 2021-01-10 reports/rbans-output.Rmd
Updates to data preprocessing and buffering

```{r preprocessing}
df_rbans <- add_session_to_rbans(df_rbans, df_demographics)
df_rbans_long <- df_rbans %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score")
df_rbans_long <- df_rbans_long %>%
  group_by(trenink, first_training, subtest) %>%
  summarise(group_avg = mean(score, na.rm = TRUE)) %>%
  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))
```
```{r}
df_ids %>%
  count(is_ok, rbans_ok, logy_ok) %>%
  kable(caption = "Overview of the state of affairs")
```

@@

df_rbans %>%
  filter(diagnosis == "schizophrenia") %>%
  ggplot(aes(session, iq_rec)) +
    geom_line(aes(color=rbansid)) +geom_point() +
    facet_wrap(~first_training)

@@

df_ids %>%
  left_join(select(df_demographics, rbansid, first_training), by = "rbansid") %>%
  count(is_ok, first_training)

>>>>

```{r preprocessing}
df_rbans <- add_session_to_rbans(df_rbans, df_demographics)
df_rbans_long <- df_rbans %>%
    pivot_longer(-c(rbansid, trenink, diagnosis, first_training, session),
                 names_to = "subtest", values_to = "score")
df_rbans_long <- df_rbans_long %>%
  group_by(trenink, first_training, subtest) %>%
  summarise(group_avg = mean(score, na.rm = TRUE)) %>%
  right_join(df_rbans_long, by = c("trenink", "first_training", "subtest"))
```
```{r}
df_ids %>%
  count(is_ok, rbans_ok, logy_ok) %>%
  kable(caption = "Overview of the state of affairs")

df_rbans_long %>%
  group_by(session) %>%
  summarise(length(unique(rbansid)))

df_ids %>%
  left_join(select(df_demographics, rbansid, first_training), by = "rbansid") %>%
  count(is_ok, first_training)
```

@@

df_rbans %>%
  filter(!is.na(first_training)) %>%
  ggplot(aes(session, vybaveniseznamu)) +
    geom_line(aes(color=rbansid)) + geom_point() +
    facet_wrap( ~ first_training + diagnosis)

@@
